Costs

### 2016-02-06 ms.tex
more integration into remake

\subsection{Immature phase}
% TODO update this to reflect what happens in the model
% ie pullign the maturation times from the logistic cdf with location and parameters given

@@

We then use this as the rate parameter $lambda$ to repeatedly draw the time of the next discovery event for this individual from the exponential distribution, we do this for each male from when they mature up to when the females matrure.
When an event occurs we select a nest randomly and then the male will either occupy it or contest another male for it.

@@

Contests can be escalated to different degrees with increasing energy costs for both participants. 
Either participant may abandon the contest at any moment, they do this by choosing not to escalate.
We assume that there are energetic costs, but that there is no time cost to contests ie they occur instantanously.

@@

@@

\begin{table}[h!]
    \caption{Variable names and definitions in the model.}
    \centering
    \begin{tabular}{c | c | l }
        \hline
        Symbol & unit & Description\\
        \hline
        \hline
        $K$ & & number of individual males \\
        $N$ & & number of nests \\
        $R_i$ & & repoductive value of nest of nest $i$\\
        $\bar{R}$ & & average repoductive value of nest\\
        \hline
        $t_m$ & & the time at which the females begin to mature\\
        $S(t)$ = exp($-k_it$) & & The probability of an individual surviving to time t.\\
        \hline
        $m$ & $g$ & mass\\
        $m_mat$ & $g$ & The size at which 50\% of the population is mature.\\
        $E$ & kJ & kiloJoules\\
        \hline
    \end{tabular}
\end{table}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=10cm,height=10cm,keepaspectratio]{figures/event_algorithm}
\caption{Algorithm for modelling dynamics within the ``mature'' male population.}
\label{fig:events}
\end{figure}
\clearpage

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=15cm,keepaspectratio]{figures/contest_algorithm}
\caption{Algorithm for modelling contests behaviour within the ``mature'' male population.}
\label{fig:contests}
\end{figure}
\clearpage

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=15cm,keepaspectratio]{figures/area_searched}
\caption{the area searched by a male in interval $dt$}
\label{fig:area searched}
\end{figure}
\clearpage

>>>>

\subsection{Immature phase}
% TODO update this to reflect what happens in the model
% ie pulling the maturation times from the logistic cdf with location and parameters given

@@

We then use this as the rate parameter $lambda$ to repeatedly draw the time of the next discovery event for this individual from the exponential distribution, we do this for each male from when they mature up to when the females mature.
When an event occurs we select a nest randomly and then the male will either occupy it or contest another male for it.

@@

Contests can be escalated to different degrees with increasing energy costs for both participants. 
Either participant may abandon the contest at any moment, they do this by choosing not to escalate.
We assume that there are energetic costs, but that there is no time cost to contests ie they occur instantaneously.

@@

\section{Results} % (fold)
\label{sec:results}

\begin{figure}[h!]
    \centering
    \includegraphics[width=8cm,height=10cm,keepaspectratio]{figures/energy_pc_plot.pdf}
    \caption{Percent energy expenditure of cohort at generation 499}
    \label{fig:energy pc}

    \centering
    \includegraphics[width=8cm,height=10cm,keepaspectratio]{figures/energy_total_plot.pdf}
    \caption{Total energy expenditure of cohort at generation 499}
    \label{fig:energy total}
\end{figure}
As patch area increases the number of fight importunities decreases, 
This can probably explain the strong decrease in energy spent fighting. but I have no idea, early days yet.

\begin{figure}[h!]
    \centering
    \includegraphics[width=10cm,height=10cm,keepaspectratio]{figures/k_density.pdf}
    \caption{a density plot of the aggression parameter k at max energy}
    \label{fig:k density}

    \includegraphics[width=10cm,height=10cm,keepaspectratio]{figures/e_0_density.pdf}
    \caption{a density plot of the aggression parameter $e_0$ at max energy}
    \label{fig:e_0 density}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=15cm,height=8cm,keepaspectratio]{figures/aggression_density.pdf}
    \caption{a density plot of aggression at max energy. I am trying to get it to be multiple plots}
    \label{fig:aggression density}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=15cm,height=10cm,keepaspectratio]{figures/num_winners.pdf}
    \caption{Number of successful males at different patch areas, gaps are because it took longer than 12 hours to run}
    \label{fig:num winners}
\end{figure}

\clearpage
% section results (end)results

@@

\begin{table}[h!]
    \caption{Variable names and definitions in the model.}
    \centering
    \begin{tabular}{c | c | l }
        \hline
        Symbol & unit & Description\\
        \hline
        \hline
        $K$ & & number of individual males \\
        $N$ & & number of nests \\
        $R_i$ & & reproductive value of nest of nest $i$\\
        $\bar{R}$ & & average reproductive value of nest\\
        \hline
        $t_m$ & & the time at which the females begin to mature\\
        $S(t)$ = exp($-k_it$) & & The probability of an individual surviving to time t.\\
        \hline
        $m$ & $g$ & mass\\
        $m_mat$ & $g$ & The size at which 50\% of the population is mature.\\
        $E$ & kJ & kiloJoules\\
        \hline
    \end{tabular}
\end{table}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=15cm,keepaspectratio]{figures/area_searched}
\caption{the area searched by a male in interval $dt$}
\label{fig:area searched figure}
\end{figure}
\clearpage

### 2016-02-06 scrap/costs.Rmd
more integration into remake

```{r}
library(rasterVis)
loser_masses <- seq(1, 100, by = 0.1)
winner_masses <- seq(1, 100, by = 0.1)
e_0 <- 0 
E_loser_max <- 100

costs <- function( m_loser, m_winner, k){
    E_loser_max / (1 + exp(-((m_winner - m_loser) / k - e_0)))
}
```
costs_scaling <- 25:
```{R}
cost_scaling <- 25 # k 
r <- raster(outer(loser_masses, winner_masses, function(a,b){costs(a, b, cost_scaling)}), 
              xmn = 0,
              xmx = 100,
              ymn = 0,
              ymx = 100)

>>>>

```{r}
library(rasterVis)
loser_masses <- seq(1, 100, by = 0.1)
winner_masses <- seq(1, 100, by = 0.1)
e_0 <- -0.5
E_loser_max <- 100

costs <- function( m_loser, m_winner, k){
    E_loser_max / (1 + exp(-((m_winner - m_loser) / k - e_0)))
}
```
costs_scaling <- 25:
```{R}
cost_scaling <- 100 # k 
r <- raster(outer(loser_masses, winner_masses, function(a,b){costs(a, b, cost_scaling)}), 
              xmn = 0,
              xmx = 100,
              ymn = 0,
              ymx = 100)
